%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend Engineer} % Job title
    {Hastega S.r.l.} % Organization
    {Lucca, Italy} % Location
    {July 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained dynamic websites for diverse clientele, ensuring optimal functionality and user experience.}
        \item {Collaborated with design teams to implement responsive and visually appealing web designs, focusing on usability and modern aesthetics.}
        \item {Implemented SEO strategies, significantly improving website visibility and search engine rankings for clients.}
        \item {Provided technical support and troubleshooting expertise to clients, resolving issues promptly to maintain client satisfaction.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Engineer} % Job title
    {Contrader} % Organization
    {Benevento, Italy} % Location
    {June 2021 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed websites, portals and large-scale web applications for multiple clients.}
        \item {Collaborated with agile development team to test, develop and maintain web and desktop-based software applications.}
        \item {Created successful websites that met requirements for objectives such as load speed and design.}
        \item {Implemented web design and development principles to build stable software.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
